Adversarial Training of Invariant Features for Speech Recognition

### 2017-03-21 interspeech/paper.tex
initial related work citations

\section{Related Work}
\label{sec:relatedwork}
    %TODO

    The effectiveness of representations produced by a neural network for internal 
    noise reduction is discussed by~\cite{yu2013feature} and this work sets a 
    baseline for experiments on the Aurora-4 dataset. Recently, 
    in a work by~\cite{yusuke2016adversarial} a multi-layer sigmoidal network was trained 
    in an adversarial fashion on an in-house transcription task corrupted by noise.

>>>>

\section{Related Work}
\label{sec:relatedwork}
    %TODO
    To be robust with respect to different recording conditions and speakers,
    one can either aim to adapt the model parameters to these new situations or
    to learn representations which are invariant to them.
    Unfortunately, many of the adaptation methods which have been designed for
    GMM-HMM systems cannot be applied to DNN-based systems. For this reason, a
    large body of recent work has investigated new adaptation methods for neural
    networks.

    The effectiveness of representations produced by a neural network for internal 
    noise reduction is discussed by~\cite{yu2013feature} and this work sets a 
    baseline for experiments on the Aurora-4 dataset.

    Some of the linear and affine transformations used for GMM adaptation can
    still be applied to neural networks when one limits these adaptations to the
    very last layer, as was shown in~ \cite{yao2012adaptation}. The
    improvements seemed to rely mostly on the adaptation of the bias parameters.

    Many neural network speaker/condition adaptation methods are based on
    i-vectors. One way to do this is by providing the i-vectors as additional
    inputs \cite{senior2014improving}.

    In the specific case of noise robustness, one can use speech enhancement to
    obtain more robust features and neural networks have been used for this for
    decades \cite{knecht1995neural}. A further step in this direction is to train
    systems to recognize speech and perform speech enhancement jointly \cite{narayanan2014joint}.

    Another strategy is to retrain the model parameters using a very small
    number of utterances from the new domain while making sure that the model
    doesn't stray too far away from the parameter values that were obtained from
    the train data \cite{yu2013kl}.
    The adaptation to new domains can also be kept under control by limiting
    the number of parameters which are adapted to the new data or by limiting the
    adaptation to a rescaling of the hidden unit activations
    \cite{swietojanski2014learning}.

    Recently, in a work by~\cite{yusuke2016adversarial} a multi-layer sigmoidal network was trained 
    in an adversarial fashion on an in-house transcription task corrupted by noise.
